Application-Level Regression Testing Framework using Jenkins

### 2017-03-02 manuscript/manuscript.tex
added some space for next page
added filesystem dashboard
wiki filesystem dashboard use case

/etc/httpd/config.d/ssl.conf:
Listen 443
<VirtualHost _default_:443>
SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
(512000) Reuben how you cache the opt?
SSLSessionCacheTimeout  300
ServerName bwjenkins.ncsa.illinois.edu:443
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

@@

>>>>

/etc/httpd/config.d/ssl.conf:
Listen 443
<VirtualHost _default_:443>
SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
SSLSessionCacheTimeout  300
ServerName bwjenkins.ncsa.illinois.edu:443
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

@@

\subsection{filesystem dashboard}
Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki.  The http:// urls for the plot images are shown on the dashboard and provide a recent-time display of filesystem metrics from a user point of view.  We add a Jenkins test to track the response time of /bin/ls on the login nodes--a reasonable metric of metadata server health and also the number one issue reported by users when we are having filesystem issues.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{wiki-dashboard}
\caption{ filesystem dashboard displaying multiple Jenkins plots }
\label{fig:wiki-dashboard}
\end{figure}
